---
title: "Sampling_Models"
author: "Umberto Fasci"
date: "4/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sampling Models

Sampling models are ubiquitous in data science.


### Casino Game Example

Casino games offer a plethora of examples of real-world situations in which sampling models are used to answer specific questions.

#### Roullete

Setting up the colors:

```{r echo=TRUE}
color <- rep(c("Black", "Red", "Green"), c(18,18,2))
```

1000 draws where red equals 1 loss for the casino and black equals 1 win for the casino.

```{r echo=TRUE}
n <- 1000
x <- sample(ifelse(color == "Red", -1, 1), n, replace = TRUE) # it's a roulette table the colors always remain there per spin.
x[1:10]
```
Now taking the Sampling Model approach to this example:

```{r echo=TRUE}
x <- sample(c(-1,1), n, replace = TRUE, prob = c(9/19, 10/19))
S <- sum(x)
S
```

S in this case is a random variable. A very important concept is the probability distribution of these random variables. This is the probability of the observed value falling in any given interval.

If we want to define a cumulative distribution function:

$$F(a) = Pr(S \le a)$$

With this we will be able to answer any question related to the probability of events defined by the random variable `S`.

Now, we can estimate the distribution function for the random variable S by using a Monte Carlo simulation to generate many realizations.

### Monte Carlo Simulation Using a Sampling Model

```{r echo=TRUE}
n <- 1000
B <- 10000
S <- replicate(B, {
  X <- sample(c(-1,1), n, replace = TRUE, prob = c(9/19, 10,19))
  sum(X)
})
mean(S < a)
```


```{r echo=TRUE}
library(tidyverse)

s <- seq(min(S), max(S), length = 100)
normal_density <- data.frame(s = s, f = dnorm(s, mean(S), sd(S)))
data.frame(S = S)%>%
  ggplot(aes(S, ..density..)) +
    geom_histogram(color = "black", binwidth = 10) +
    ylab("Probability") +
    geom_line(data = normal_density, mapping = aes(s, f), color = "blue")
```

